Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-08-29 WSSSPE3/report/WSSSPE3_review.tex
changing in-line reference to footnote with full clickable URL

\item \textbf{Alice Allen: \textit{We're giving away the store! (Merchandise not
included)}}. Alice Allen described the Astrophysics Source Code Library
(ascl.net), an increasingly used way to obtain a unique ID for astrophysics
software that is indexed by indexing services and can be cited. ASCL offers
clones of existing infrastructure, provides server space and computing
resources, shares innovations, and permits moves elsewhere. Users provide a
domain name, then control and configure their site and use it as intended,
gather their codes as they wish, share innovations, and protect the provided
computing environment.

>>>>

\item \textbf{Alice Allen: \textit{We're giving away the store! (Merchandise not
included)}}. Alice Allen described the Astrophysics Source Code Library\footnote{\url{http://ascl.net}}, an increasingly used way to obtain a unique ID for astrophysics
software that is indexed by indexing services and can be cited. ASCL offers
clones of existing infrastructure, provides server space and computing
resources, shares innovations, and permits moves elsewhere. Users provide a
domain name, then control and configure their site and use it as intended,
gather their codes as they wish, share innovations, and protect the provided
computing environment.
